---
title: "Alcohol vs Seat choice"
author: "davy.d"
date: "spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
ucdavis1 <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

# Introduction

Data is from the UCDavis.csv
Is the average amount of alcohol consumed per week different for the different seating rows.

$H_0$: there is no difference in the average amount of alcohol consumed per week based on different seating rows.

$H_A$: there is a difference in average alcohol consumed per week based on different between at least two seating rows.
# Methods

We predict alcohol consumption based on row. 
alcohol ~ Seat

Data from UC Davis:
alcohol is a numerical variable. 
Seat is a categorical variable.
so we use the numerical ~ cat helper file.

# Description
## graphical description

```{r}
boxplot(alcohol~Seat,data=ucdavis1)
```


this box plot shows that people sitting in the back row tend to drink more


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(ucdavis1,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


